\section{Installation}
PseudoID is designed to be installed on Windows computers and requires administrator privileges (i.e authorization from the IT department, for each installation individually).

\begin{itemize}
    \item Click \href{https://github.com/spisakt/PseudoID/releases}{\underline{here}} to access the latest version of PseudoID.
    \item Download the following files to an arbitrary folder\footnote{If you can not see the file extensions, you should activate them under "View" in the explorer}: 
    \begin{itemize}
        \item \path{start_pseudoid.exe}
        \item \path{pseudoid.txt}
        \item \path{handler.txt}
        \item \path{settings.conf} 
    \end{itemize}
    \item If you have administrator privileges on the computer, simply double-click the file called \path{start_pseudoid.exe} to start the software.
    
    Refer to the instructions below if you are working on a centrally administered computer.
\end{itemize} 

\subsection*{Installation on centrally-administered computers}

Please contact the IT department (via phone call or ticket) and ask for privileges for running the software. Explain the IT department what the software exactly does: "PseudoID is a research software for SFB289. Technical details: it is a flask application deployed as a standalone exe file. It reads two configuration files from the same folder and runs a webserver on the localhost (Port 5000)".

As an additional information. you can provide the following steps, which worked at the University Hospital Essen.

\begin{enumerate}
    
    \item The administrator from the IT department should move \path{start_pseudoid.exe}, \path{handler.txt} and \path{settings.conf} to a directory, from which the \path{.exe} can be executed. Caution: They have to be in the SAME folder. 
    
    \item The \path{pseudoid.txt} file should be moved to a location that can be accessed by the user, for example the desktop. The file should then be opened with the basic text editor, to change the current path to the path where the \path{.exe} was moved to
    \label{item:admin}
    
    \item For example: the current \path{pseudoid.txt} ends like this: \\ \path{.\pseudoid.exe}. \\ This should be changed to the NEW path of the \path{start_pseudoid.exe}
    
    \item When this has been changed correctly, the file name of \path{pseudoid.txt} has to be changed to \path{start_pseudoid.bat} (you can ignore the warning)
    
    \item If everything worked out properly, a double-click on \path{start_pseudoid.bat} should start PseudoID in a new browser window!
    
    \item The command line window can be closed, when PseudoID is closed.
\end{enumerate} 


